An investigation into using scagnostics to find interesting projections of high-dimensional data

### 2018-10-19 scagnostics.Rmd
Added small study on rotation dependence.

>>>>

## Rotation dependence
\textcolor{red}{testin rotation dependence by turning sine dataset with $\alpha \in [0,2\pi]$}
Interesting to note that some indexes are symmetric around $\pi$, but scagnostics indexes are very arbitrary, dependence is introduced via binnibng (and outlier removal?) here. Observe huge drops for some of the indexes! 
```{r rotationDep, fig.width=6, fig.height=7, fig.cap="Rotation dependence of the considered index functions tested on the sine 1000 dataset, by rotating the special view by an angle alpha."}
sineM <- as.matrix(select(sin1000, V5, V6))
sc <- tibble(
    holes=numeric(),
    cmass=numeric(),
    convex=numeric(),
    skinny=numeric(),
    stringy=numeric(),
    dcor2d=numeric(),
    splines2d=numeric(),
    MIC=numeric(),
    TIC=numeric(),
    alpha=numeric()
)
for (a in seq(0,2*pi, pi/20)){
  rotM <- matrix(c(cos(a), sin(a), -sin(a), cos(a)), ncol = 2)
  dprj <- sineM %*% rotM
  scagRes <- scagnostics(dprj)
  dcorRes <- dcor2d(dprj[,1], dprj[,2])
  splineRes <- splines2d(dprj[,1], dprj[,2])
  mineRes <- mine(dprj[,1], dprj[,2])
  holesRes <- holes(dprj)
  cmassRes <- cmass(dprj)
  sc <- add_row(sc, holes=holesRes, cmass=cmassRes,
                convex=scagRes[,"Convex"], skinny=scagRes[,"Skinny"],
                stringy=scagRes[,"Stringy"], dcor2d=dcorRes,
                splines2d=splineRes, MIC=mineRes$MIC,
                TIC=mineRes$TIC, alpha=a)
  }

scMelt <- melt(sc, id=c("alpha"))
ggplot(scMelt, aes(x=alpha, y=value)) +
  geom_line() + 
  facet_wrap(~variable, scales = "free_y", ncol = 1)
```
